A thesis draft

### 2018-11-28 res/sections/40-FutureWork.tex
Finish future work draft

The importance of having NS services updated as smooth as possible.

>>>>

The importance of having NS services updated as smooth as possible is without 
doubts a feature that would ensure a continue service availability avoiding its 
disruption. This kind of approach, though, requires particular attention about 
keeping the current connections alive. This means at least keeping the old 
chain up while deploying the new one, and gradefully redirect all the 
new traffic from the chain to replace, until none is left. Only after this 
operation, the old chain definition can be completely decomissioned and the 
related VNFs removed. In our current implementation, the NS update 
functionality relies on a simpler approach: when an update gets ordered, 
Kubernetes gets instructed to remove the old chain and deploy the new one. 
Meanwhile, all the Roulette controllers get updated with the new NS route. The 
back of the medal of this soulution is, while it keeps the sistem implementation 
simpler, that packets current travelling along the old NS could be lost during 
the chain updating.
